The necessity of hypermedia RDF and an approach to achieve it

### 2012-03-01 eswc-2012/workshop2.tex
trim paragraph about URI structure trim triples
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@148 43ef1190-90fd-4dd7-a769-d0121f02b80e

In a read-only situation, the HATEOAS constraint requires that the
application can navigate from one resources to another using the
hypermedia links in the present resource \emph{only}, it should not
require any out-of-band information to do so. Thus, a RESTful protocol
should not require prior knowledge of a URI structure, but one may
define the protocol in terms of URI structure as long as the same
information can be gleaned from the resources. Nor does it require
that all resources can be reached from any other resource. As such,
the constraint is not very strict, one could argue that as long as
there are some links, the protocol satisfies the HATEOAS constraint.

@@

\begin{verbatim}
<> hm:canBe hm:replaced ,
            hm:deleted .
\end{verbatim}

@@

E.g.

\begin{verbatim}
hm:replaced        hm:httpMethod "PUT" .
hm:deleted         hm:httpMethod "DELETE" .
hm:mergedInto      hm:httpMethod "POST" .
hm:createSimilarAt hm:httpMethod "POST" .
\end{verbatim}

>>>>

In a read-only situation, the HATEOAS constraint requires that the
application can navigate from one resources to another using the
hypermedia links in the present resource \emph{only}, it should not
require any out-of-band information.

@@

\begin{verbatim}
<> hm:canBe hm:replaced, hm:deleted .
\end{verbatim}

@@

For example (with similar triples for other HTTP methods):
\begin{verbatim}
hm:replaced hm:httpMethod "PUT" .
\end{verbatim}
